---
title: "EDLD 610 Spring 2020 Final Project Outline"
author: "Claire Zhang; JP Pedroza; Thuy Nguyen; Jim Wright"
date: "4/16/2020"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: "spacelab"
    highlight: "tango"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rio)
library(here)
library(tidyverse)

safe <- import(here("data", "2006_school_safety.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() 

safe06 <- import(here("data", "2006_school_safety_v2.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() 

safe08 <- import(here('data', '2008_school_safety.sav'),
                 setclass = 'tbl_df') %>% 
  characterize() %>% 
  janitor::clean_names()
```

### Chosen Format
For our final project, we intend to use a shiny application. 


### Purpose 
The purpose of our final project will be substantive and include a final product that could be utilized by a client, such as an educational agency. 


### Description of the Data 
The data for our project comes from the 2005-2006 School Survey on Crime and Safety. The data was obtained via [data.gov](https://catalog.data.gov/dataset/2006-school-survey-on-crime-and-safety) and is a large SPSS file with 2,724 rows by 525 columns. The goal of our project will be to explore the relation between various variables within the data set. Specifically, four categorical variables we intend to use in models include: _school enrollment_, _minority percentage school enrollment_, _school urbanicity_, _school level_. These variables will be modeled to predict the following quantitative outcome variable: _out of school suspensions_. Further, we will explore the relation between the provision of teacher training on predicting out of school suspensions as well as the relation between the aforementioned categorical variables on predicting the provision of teacher training. The teacher training variables are logical with a binary yes/no coded response. We intend for our final product to identify trends that would be helpful for school administrations to identify what types of teacher trainings may prevent out of school suspensions. 


### Some variables of interest
Protecting measures (IDs): 

C0146 Security camera(s) monitor the school
C0174 Prevention curriculum/instruction/training
C0178 Student counseling/social work

Outcomes (DVs): 

C0308 School shooting incidents
C0326 Number of attacks with weapon - total
C0346 Number of possession of firearms - total
C0376 How often student bullying occurs
C0378 How often student sexual harassment of student
C0380 How often student verbal abuse of teachers

### Lingering Questions

# JP's note:
Hey all, while I was looking into the SSOCS data, the main data source is at [The National Center for Education Statistics](https://nces.ed.gov/surveys/ssocs/index.asp). I found that the data in this file has a similar file for the following cycle (07-08). I thought since we are in interested in a shiny app, which includes dropdown menus to show differences, we could have a dropdown menu that shows our models between the year cycles. This is just a thought and it wouldn't add much to our work but would add more to the implications of the app. 

# Claire's thoughts:

1. Data description - we probably want to start with this:
The School Survey on Crime and Safety (SSOCS) is the primary source of school-level data on crime and safety for the U.S. Department of Education, National Center for Education Statistics (NCES). It is a nationally representative survey of about 4,800 public elementary and secondary schools and there'are several waves of data available at https://nces.ed.gov/surveys/ssocs/data_products.asp#1999, from SY 1999-2000 to SY 17-18. 

2. About our shiny app - it can be so much fun:
After consultation with Daniel and going though the shiny app he shared with us today (4/29), I really think we can do something just like that. 

For example, we can take advantage of the several waves available, say 05-06, 07-08, 15-16, 17-18, and see through how the variables of our interest and their relationships evolve over years. We can produce a shiny app just like Daniel did: put each variable (e.g., verbal abuse of teachers) or each correlation (e.g., urbanicity and out of school suspensions) into the dropdown mane and give readers view options like "four year total", "compare 05-06 and 15-16", "compare 07-08 and 17-18", "by year", or even "by grade", etc.

The four waves of data are here:

```{r}
sf06 <- import(here("data", "pu_ssocs06_spss.sav"),
               setclass = "tbl_df") 
sf08 <- import(here("data", "pu_ssocs08_spss.sav"),
               setclass = "tbl_df") 
sf16 <- import(here("data", "pu_ssocs16.sas7bdat"),
               setclass = "tbl_df")
sf18 <- import(here("data", "pu_ssocs18.sav"),
               setclass = "tbl_df")

```

Looking forward to your thoughts!