---
title: "Organized Shiny Code"
author: "Thuy Nguyen, JP Pedroza, Jim Wright, and Claire Zhang"
date: "5/25/2020"
output: html_document
---

Stephanie Gluck Peer Review 

Area of Strength:

1) I learned about the `readr::parse_number` and thought this was a neat function. I checked out the help documentation for `parse_number` and can see myself using this function in my own work. 

2) I think a shiny app is very fitting for this large dataset as it will allow the audience to select data and visualize trends that they are interested in examining. 

3) I found the idea to incorporate a stop function in the code to check for the structure of the input variable to be really useful and I was curious as to how error messages can be incorporated into shiny app as that would proably be beneficial for the users of the shiny app too. 

What I learned from reviewing the project: 

Similar to the other group's project that I reviewed, it strikes me the sheer amount of data that is generated in a large national education dataset compared to work in my field where the sample sizes are typically much smaller. Given the large amount of data, having function will be immensely helpful at subsetting and looping through a variable of interest such as year in this case. 

Area of Improvement (see codes in their respective code chunk): 

1) I included minor formatting codes for rounding values in your potential output table and wrapped output table in `gt` or `reactable`. Also included code to move the legend to bottom of plot in ggplot. 

2) I noticed there was a stop function included in the custom function (really good idea!) `numeric_plot` and I tried to test the stop function but it appears the plot still ran (it is possible I am not understanding the stop function correctly). I was not sure if this is something important for the shiny app. 

3) It may be informative for the plots in "step 3, nest by year and visualize school safety, size, and urbanicity" to have title that inclues the year. I was not able to come up with a code for this (sorry) but I know that the codes were covered in our "Parallel iterations" lecture. 





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(rio)
library(fs)
library(ggridges)
library(glue)
# devtools::install_github("gadenbuie/regexplain")
```

Background:
This project will be a shiny app that will provide a quick look into data from three different years of the School Survey on Crime and Safety (05-06, 07-08, 17-18). The app will provide users with all the variables from these datasets that are matched between the different years. We are hoping that this shiny app will be able to provide general associations between continuous variables while being able to choose which year of the dataset the user is interested in as well as looking at differences between categories for any variable of interest. We are currently working on the shiny app and any feedback would be greatly appreciated, especially with the functions as they will be the base for the shiny app.


```{r data upload}
files <- dir_ls(here::here("data"), glob = "*.csv")

batch <- map_df(files, read_csv)
batch

batch <- batch %>% 
  mutate(fr_ubran = as.factor(fr_urban),
         fr_size = as.factor(fr_size),
         year = as.factor(c0578_yy))
```

```{r}
batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(mean_score = map_dbl(data, ~mean(.x$c0534))) %>% 
  ggplot(aes(year, mean_score)) +
  geom_col()

```

```{r parallel iteration}
comparing <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model_1 = map(data, ~lm(c0534 ~ fr_urban, data = .x)),
         model_2 = map(data, ~lm(c0534 ~ fr_size, data = .x))) %>% 
  mutate(model_compare = map2(model_1, model_2, stats::AIC),
         aic_model_1 = map_dbl(model_compare, list('AIC', 1)),
         aic_model_2 = map_dbl(model_compare, list('AIC', 2)))

compare_plot <- comparing %>% 
  dplyr::select(year, aic_model_1, aic_model_2) %>% 
  pivot_longer(-year, names_to = 'year_AIC', values_to = 'values') %>% 
  mutate_if(is.numeric, round, 3) # if you want to round your AIC values 

#I am not sure how you were planning to integrate the table into the shiny app but perhaps using gt or reactable could be a way. 
reactable::reactable(compare_plot)
gt::gt(compare_plot)

```

```{r nest and mutate}
models <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(c0534 ~ c0562, data = .x))) %>% 
  pivot_longer(model, names_to = 'model', values_to = 'output') %>% 
  mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))

```


```{r}
# Function 1
numeric_plot <- function(df, x, y){
  plot_num <- ggplot({{df}}, aes({{x}}, {{y}})) +
      geom_point(alpha = .4, color = 'gray70') +
      geom_smooth(method = 'lm')
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_num
  }
  return(plot_num)
}

numeric_plot(batch, batch$c0534, batch$c0536) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

#I tried to plot using non numerics to test the stop function but it seems that the plot still runs (perhaps I am not interpreting the stop criteria correctly), not sure how important this will be for the actual shiny app. 
numeric_plot(batch, batch$fr_size, batch$fr_urban) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

is.numeric(batch$fr_size)
is.numeric(batch$fr_urban)
is.numeric(batch$c0534)

```

```{r}
# Function 2
bar_plot <- function(df, x, y, fill){
  plot_cat <- ggplot({{df}}, aes({{x}}, {{y}}, {{fill}})) +
  geom_col() +
  coord_flip()
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_cat
  }
return(plot_cat)
}

bar_plot(batch, batch$fr_urban, batch$c0534, fill = batch$fr_urban) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

```



### Nest and Mutate (Claire Zhang)

I'll use the original four years' datasets (05-06, 07-08, 15-16, 17-18) from the NCES website, https://nces.ed.gov/surveys/ssocs/, and select variables of interest that are available across all four years including urbanicity, school size, percentage of low-performing students, percentage of college-going students, and total numbers of a) incidents reported, b) incidents reported to police, and c) out-of-school suspensions.

step 1, prepare four-year data:

```{r}
sf06 <- import(here("data_1", "pu_ssocs06_spss.sav"),
               setclass = "tbl_df") %>%
        select(urbanicity = FR_LOC4,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID06,
               incidents_police = INCPOL06,
               suspension = OUTSUS06) %>% 
        mutate(year = "2006")
sf08 <- import(here("data_1", "pu_ssocs08_spss.sav"),
               setclass = "tbl_df") %>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID08,
               incidents_police = INCPOL08,
               suspension = OUTSUS08)%>% 
        mutate(year = "2008")
sf16 <- import(here("data_1", "pu_ssocs16.sas7bdat"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID16,
               incidents_police = INCPOL16,
               suspension = OUTSUS16)%>% 
        mutate(year = "2016")
sf18 <- import(here("data_1", "pu_ssocs18.sav"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID18,
               incidents_police = INCPOL18,
               suspension = OUTSUS18)%>% 
        mutate(year = "2018")
four_year <- bind_rows(sf06, sf08, sf16, sf18)%>%
  pivot_longer(cols = c(incidents, incidents_police, suspension),
                          names_to = "safety_indicators",
                          values_to = "total") %>% 
  mutate(urbanicity = recode(urbanicity, '1' = "City", '2' = "Suburb", '3' = "Town", '4' = "Rural"),
         size = recode(size, '1' = "<300", '2' = "300-499", '3' = "500-999", '4' = "1,000+"),
         size = fct_relevel(size, "<300", "300-499", "500-999", "1,000+"))

```

step 2, inspect the four year data

```{r}
full_plot1 <- four_year %>%
  group_by(year, safety_indicators) %>% 
  mutate(mean = mean(total)) %>% 
  ungroup() %>% 
  mutate(year = readr::parse_number(year)) %>% 
  ggplot(aes(year, mean))+
  geom_line(aes(color = safety_indicators), size = 0.9)+
  geom_point()+
  labs(title = "School Safety from 2006 to 2018",
       x = "School Year",
       y = "Average Number of Cases in School",
       fill = "Safety Indicators")

full_plot1

```

step 3, nest by year and visualize school safety, size, and urbanicity

```{r}
plot1 <- function(x){
  x %>%
    ggplot(aes(size, total))+
    geom_col(aes(fill = safety_indicators),
             position = "dodge")+
    facet_wrap(~urbanicity)+
    theme_minimal()+
    scale_fill_brewer(palette = "Set2")+
    labs(title = "School Safety, School Size, and Urbanicity",
         x = "School Size",
         y = "Total Number of Cases",
         fill = "Safety Indicators") +
    theme(legend.position = "bottom") # if you want to move your legend to the bottom of the plot 
}

plot1(four_year)

plot1_by_year <- four_year %>% 
  group_by(year) %>%
  nest() %>% 
  mutate(plot = map(data, ~plot1(.x)))

plot1_by_year$plot[[1]]
plot1_by_year$plot[[2]]
plot1_by_year$plot[[3]]
plot1_by_year$plot[[4]]


```

```{r walk reduce or modify used}

fs::dir_create(here::here("plots_1", "indicators"))


files <- plot1_by_year$year
paths <- here::here("plots_1", "indicators", glue("{files}.png"))
paths

walk2(paths, plot1_by_year$plot, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```


