---
title: "Organized Shiny Code"
author: "Thuy Nguyen, JP Pedroza, Jim Wright, and Claire Zhang"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(rio)
library(fs)
library(ggridges)
library(glue)
# devtools::install_github("gadenbuie/regexplain")
```

Background:
This project will be a shiny app that will provide a quick look into data from three different years of the School Survey on Crime and Safety (05-06, 07-08, 17-18). The app will provide users with all the variables from these datasets that are matched between the different years. We are hoping that this shiny app will be able to provide general associations between continuous variables while being able to choose which year of the dataset the user is interested in as well as looking at differences between categories for any variable of interest. We are currently working on the shiny app and any feedback would be greatly appreciated, especially with the functions as they will be the base for the shiny app.


```{r data upload}
files <- dir_ls(here::here("data"), glob = "*.csv")

batch <- map_df(files, read_csv)
batch

batch <- batch %>% 
  mutate(fr_ubran = as.factor(fr_urban), # AGI: is fr_ubran a typo? Did you mean fr_urban? If you don't change it you will have a variable called fr_urban (column 96) that is type character and a variable called fr_ubran that is type factor (column 189).
         fr_size = as.factor(fr_size),
         year = as.factor(c0578_yy))
```

```{r}
batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(mean_score = map_dbl(data, ~mean(.x$c0534))) %>% 
  ggplot(aes(year, mean_score)) +
  geom_col()

```

```{r parallel iteration}
comparing <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model_1 = map(data, ~lm(c0534 ~ fr_urban, data = .x)),
         model_2 = map(data, ~lm(c0534 ~ fr_size, data = .x))) %>% 
  mutate(model_compare = map2(model_1, model_2, stats::AIC),
         aic_model_1 = map_dbl(model_compare, list('AIC', 1)),
         aic_model_2 = map_dbl(model_compare, list('AIC', 2)))

compare_plot <- comparing %>% 
  dplyr::select(year, aic_model_1, aic_model_2) %>% 
  pivot_longer(-year, names_to = 'year_AIC', values_to = 'values')

```

```{r nest and mutate}
models <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(c0534 ~ c0562, data = .x))) %>% 
  pivot_longer(model, names_to = 'model', values_to = 'output') %>% 
  mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))

```


```{r}
# Function 1
numeric_plot <- function(df, x, y){
  plot_num <- ggplot({{df}}, aes({{x}}, {{y}})) +
      geom_point(alpha = .4, color = 'gray70') +
      geom_smooth(method = 'lm')
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_num
  }
  return(plot_num) # AGI: if you want to save space, you could omit this
}

numeric_plot(batch, batch$c0534, batch$c0536) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

```

```{r}
# Function 2
bar_plot <- function(df, x, y, fill){
  plot_cat <- ggplot({{df}}, aes({{x}}, {{y}}, {{fill}})) +
  geom_col() +
  coord_flip()
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_cat
  }
return(plot_cat) # AGI: if you want to save space, you could omit this
}

bar_plot(batch, batch$fr_urban, batch$c0534, fill = batch$fr_urban) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

```



### Nest and Mutate (Claire Zhang)

I'll use the original four years' datasets (05-06, 07-08, 15-16, 17-18) from the NCES website, https://nces.ed.gov/surveys/ssocs/, and select variables of interest that are available across all four years including urbanicity, school size, percentage of low-performing students, percentage of college-going students, and total numbers of a) incidents reported, b) incidents reported to police, and c) out-of-school suspensions.

step 1, prepare four-year data:

```{r}
sf06 <- import(here("data_1", "pu_ssocs06_spss.sav"), # AGI: you may want to consider reducing this code as is repetitive. You could do a batch load like you did on lines 23 to 33. 
               setclass = "tbl_df") %>%
        select(urbanicity = FR_LOC4,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID06,
               incidents_police = INCPOL06,
               suspension = OUTSUS06) %>% 
        mutate(year = "2006")
sf08 <- import(here("data_1", "pu_ssocs08_spss.sav"),
               setclass = "tbl_df") %>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID08,
               incidents_police = INCPOL08,
               suspension = OUTSUS08)%>% 
        mutate(year = "2008")
sf16 <- import(here("data_1", "pu_ssocs16.sas7bdat"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID16,
               incidents_police = INCPOL16,
               suspension = OUTSUS16)%>% 
        mutate(year = "2016")
sf18 <- import(here("data_1", "pu_ssocs18.sav"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID18,
               incidents_police = INCPOL18,
               suspension = OUTSUS18)%>% 
        mutate(year = "2018")
four_year <- bind_rows(sf06, sf08, sf16, sf18)%>%
  pivot_longer(cols = c(incidents, incidents_police, suspension),
                          names_to = "safety_indicators",
                          values_to = "total") %>% 
  mutate(urbanicity = recode(urbanicity, '1' = "City", '2' = "Suburb", '3' = "Town", '4' = "Rural"),
         size = recode(size, '1' = "<300", '2' = "300-499", '3' = "500-999", '4' = "1,000+"),
         size = fct_relevel(size, "<300", "300-499", "500-999", "1,000+"))

```

step 2, inspect the four year data

```{r}
full_plot1 <- four_year %>%
  group_by(year, safety_indicators) %>% 
  mutate(mean = mean(total)) %>% 
  ungroup() %>% 
  mutate(year = readr::parse_number(year)) %>% 
  ggplot(aes(year, mean))+
  geom_line(aes(color = safety_indicators), size = 0.9)+
  geom_point()+
  labs(title = "School Safety from 2006 to 2018",
       x = "School Year",
       y = "Average Number of Cases in School",
       fill = "Safety Indicators")

full_plot1
```

step 3, nest by year and visualize school safety, size, and urbanicity

```{r}
plot1 <- function(x){ 
  x %>%
    ggplot(aes(size, total))+
    geom_col(aes(fill = safety_indicators),
             position = "dodge")+
    facet_wrap(~urbanicity)+
    theme_minimal()+
    scale_fill_brewer(palette = "Set2")+
    labs(title = "School Safety, School Size, and Urbanicity",
         x = "School Size",
         y = "Total Number of Cases",
         fill = "Safety Indicators")
}

plot1(four_year)

plot1_by_year <- four_year %>% 
  group_by(year) %>%
  nest() %>% 
  mutate(plot = map(data, ~plot1(.x))) # AGI: I have added an alternative way of producing these plots using pmap so you could add the year of each plot at the bottom

plot1_by_year$plot[[1]]
plot1_by_year$plot[[2]]
plot1_by_year$plot[[3]]
plot1_by_year$plot[[4]]
```

```{r walk reduce or modify used}

fs::dir_create(here::here("plots_1", "indicators"))


files <- plot1_by_year$year
paths <- here::here("plots_1", "indicators", glue("{files}.png"))
paths

walk2(paths, plot1_by_year$plot, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

Peer feedback 

* Areas of strength

(1) Super interesting data set, nice find! Sounds great that you want to make this something useful for school administrators. 
(2) Well organized and readable code. I understood what you did at every step.
(3) I really liked your full_plot1; is very informative and looks nice. I suggest you set the theme to theme_set(theme_minimal()) if you want an extra pro look. 

* From reviewing your script I learned that you can select and rename variables in the same step just using select(). I will definitely use that in the future! 

* Areas for improvement:

- As per final project guidelines, I suggest you take out repetitive code in lines 131 to 170. I think you should be able to use batch load as you did at the begginning. 
- I noted some inconsistencies in spacing, you may want to look into that. 

```{r}
# alternative to lines 203 to 222
plot_by_year_df <- four_year %>%
  group_by(year) %>%
  mutate(label =
        glue("SSOCS Data from {str_to_title(year)}"))


plot_by_year <- plot_by_year_df %>%
  group_by(year, label) %>%
  nest() %>%
  mutate(plots = pmap(list(data, year, label),
                      ~ ggplot(..1, aes(size, total)) +
                        geom_col(aes(fill = safety_indicators),
             position = "dodge")+
    facet_wrap(~urbanicity)+
    theme_minimal()+
    scale_fill_brewer(palette = "Set2")+
    labs(title = glue("School Safety, School Size, and Urbanicity Year {..2}"),
         x = "School Size",
         y = "Total Number of Cases",
         fill = "Safety Indicators",
         caption = ..3)))

plot_by_year$plots[[1]]
plot_by_year$plots[[2]]
```

