---
title: "Organized Shiny Code"
author: "Thuy Nguyen, JP Pedroza, Jim Wright, and Claire Zhang"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(rio)
library(fs)
library(ggridges)
library(glue)
library(reactable)
# devtools::install_github("gadenbuie/regexplain")
```

Background:
This project will be a shiny app that will provide a quick look into data from three different years of the School Survey on Crime and Safety (05-06, 07-08, 17-18). The app will provide users with all the variables from these datasets that are matched between the different years. We are hoping that this shiny app will be able to provide general associations between continuous variables while being able to choose which year of the dataset the user is interested in as well as looking at differences between categories for any variable of interest. We are currently working on the shiny app and any feedback would be greatly appreciated, especially with the functions as they will be the base for the shiny app.


```{r data upload}
files <- dir_ls(here::here("data"), glob = "*.csv")

batch <- map_df(files, read_csv)
batch

batch <- batch %>% 
  mutate(fr_ubran = as.factor(fr_urban),
         fr_size = as.factor(fr_size),
         year = as.factor(c0578_yy))
```

```{r}
batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(mean_score = map_dbl(data, ~mean(.x$c0534))) %>% 
  ggplot(aes(year, mean_score)) +
  geom_col()

```

```{r parallel iteration}
comparing <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model_1 = map(data, ~lm(c0534 ~ fr_urban, data = .x)),
         model_2 = map(data, ~lm(c0534 ~ fr_size, data = .x))) %>% 
  mutate(model_compare = map2(model_1, model_2, stats::AIC),
         aic_model_1 = map_dbl(model_compare, list('AIC', 1)),
         aic_model_2 = map_dbl(model_compare, list('AIC', 2)))

compare_plot <- comparing %>% 
  dplyr::select(year, aic_model_1, aic_model_2) %>% 
  pivot_longer(-year, names_to = 'year_AIC', values_to = 'values')

```

#c0534: Percent students likely to go to college
#c0536: Percent students academic achievement important
#c0534: Crime where school located

#Model predicts effects of crime on the likelihood of students go to college. 

```{r nest and mutate}
models <- batch %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(c0534 ~ c0562, data = .x))) %>% 
  pivot_longer(model, names_to = 'model', values_to = 'output') %>% 
  mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))
```


```{r}
# Function 1
numeric_plot <- function(df, x, y){
  plot_num <- ggplot({{df}}, aes({{x}}, {{y}})) +
      geom_point(alpha = .4, color = 'gray70') +
      geom_smooth(method = 'lm')
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_num
  }
  return(plot_num)
}

numeric_plot(batch, batch$c0534, batch$c0536) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)


```

```{r}
# Function 2
bar_plot <- function(df, x, y, fill){
  plot_cat <- ggplot({{df}}, aes({{x}}, {{y}}, {{fill}})) +
  geom_col() +
  coord_flip()
  
  if(!as.numeric({{x}}) & !as.numeric({{y}})){
    stop()
  }
  else{
    plot_cat
  }
return(plot_cat)
}

bar_plot(batch, batch$fr_urban, batch$c0534, fill = batch$fr_urban) +
  labs(x = 'X Value',
       y = 'Y Value',
       Title = 'A Title',
       caption = 'R2') +
  facet_wrap(~year)

```



### Nest and Mutate (Claire Zhang)

I'll use the original four years' datasets (05-06, 07-08, 15-16, 17-18) from the NCES website, https://nces.ed.gov/surveys/ssocs/, and select variables of interest that are available across all four years including urbanicity, school size, percentage of low-performing students, percentage of college-going students, and total numbers of a) incidents reported, b) incidents reported to police, and c) out-of-school suspensions.

step 1, prepare four-year data:

```{r}
sf06 <- import(here("data_1", "pu_ssocs06_spss.sav"),
               setclass = "tbl_df") %>%
        select(urbanicity = FR_LOC4,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID06,
               incidents_police = INCPOL06,
               suspension = OUTSUS06) %>% 
        mutate(year = "2006")
sf08 <- import(here("data_1", "pu_ssocs08_spss.sav"),
               setclass = "tbl_df") %>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID08,
               incidents_police = INCPOL08,
               suspension = OUTSUS08)%>% 
        mutate(year = "2008")
sf16 <- import(here("data_1", "pu_ssocs16.sas7bdat"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID16,
               incidents_police = INCPOL16,
               suspension = OUTSUS16)%>% 
        mutate(year = "2016")
sf18 <- import(here("data_1", "pu_ssocs18.sav"),
               setclass = "tbl_df")%>% 
        select(urbanicity = FR_URBAN,
               size = FR_SIZE,
               low_performing = C0532,
               college_going = C0534,
               incidents = INCID18,
               incidents_police = INCPOL18,
               suspension = OUTSUS18)%>% 
        mutate(year = "2018")
four_year <- bind_rows("05-06" = sf06, "07-08" = sf08, "15-16" = sf16, "17-18" = sf18, .id = "dataset") %>%
  pivot_longer(cols = c(incidents, incidents_police, suspension),
                          names_to = "safety_indicators",
                          values_to = "total") %>% 
  mutate(urbanicity = recode(urbanicity, '1' = "City", '2' = "Suburb", '3' = "Town", '4' = "Rural"),
         size = recode(size, '1' = "<300", '2' = "300-499", '3' = "500-999", '4' = "1,000+"),
         size = fct_relevel(size, "<300", "300-499", "500-999", "1,000+"))

```

step 2, inspect the four year data

```{r}
head(four_year)
four_year$year

full_plot1 <- four_year %>%
  group_by(year, safety_indicators) %>% 
  mutate(mean = mean(total)) %>% 
  ungroup() %>% 
  mutate(as.factor(year = readr::parse_number(year))) %>% # add as.factor to try
  ggplot(aes(year, mean))+
<<<<<<< Updated upstream
  geom_line(aes(color = safety_indicators), size = 0.9)+
  geom_point() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  scale_x_continuous(limits = c(2004, 2020),
                     breaks = c(2006, 2008, 2010, 2012, 2014, 2016, 2018)) +
=======
  geom_line(aes(color = safety_indicators), size = 0.9)+ # can we change here 
  geom_point()+
>>>>>>> Stashed changes
  labs(title = "School Safety from 2006 to 2018",
       x = "School Year",
       y = "Average Number of Cases in School",
       fill = "Safety Indicators") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text(size = 10),
        axis.title=element_text(size=10))

full_plot1


# Thuy: try date time for x axis
```

step 3, nest by year and visualize school safety, size, and urbanicity

```{r}
plot1 <- function(x){
  x %>%
    ggplot(aes(size, total))+
    geom_col(aes(fill = safety_indicators),
             position = "dodge")+
    facet_wrap(~urbanicity)+
    theme_minimal()+
    scale_fill_brewer(palette = "Set2")+
    labs(title = "School Safety, School Size, and Urbanicity",
         x = "School Size",
         y = "Total Number of Cases",
         fill = "Safety Indicators")
}

plot1(four_year)

plot1_by_year <- four_year %>% 
  group_by(year) %>%
  nest() %>% 
  mutate(plot = map(data, ~plot1(.x)))

plot1_by_year$plot[[1]]
plot1_by_year$plot[[2]]
plot1_by_year$plot[[3]]
plot1_by_year$plot[[4]]

```

```{r iteration}
#tried but failed
# creating label
#want to iterate the year above

tmpt_data <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(label = 
           glue("Year {str_to_title(year)}"))

# creat plot for 4 years - tried but failed
final_plot <- tmpt %>% 
  group_by(year, label) %>% 
  nest() %>% 
  mutate(plots = pmap(list(tmpt_data, label),
                      ~ggplot(..1, aes(size, total))+
                        geom_col(aes(fill = safety_indicators),
                         position = "dodge")+
                facet_wrap(~urbanicity)+
                theme_minimal()+
                scale_fill_brewer(palette = "Set2")+
                labs(title = "School Safety, School Size, and Urbanicity",
                     x = "School Size",
                     y = "Total Number of Cases",
                     fill = "Safety Indicators",
                     caption = ..2)))
```



```{r walk reduce or modify used}

fs::dir_create(here::here("plots_1", "indicators"))


files <- plot1_by_year$year
paths <- here::here("plots_1", "indicators", glue("{files}.png"))
paths

walk2(paths, plot1_by_year$plot, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```


```{r}
head(four_year)
# i'm trying to understand what "collage bound" is 
college_bound_hist <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(plots = pmap(list(year, data), 
  ~ggplot(..2, aes(college_going)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~urbanicity) +
  theme_minimal(base_size = 15) +
  scale_x_continuous("Percentage of Students", labels = function(x) paste0(x, "%")) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  labs(x = "Percentage of Students College Bound",
       y = "Number of Schools", # "Total number of students across areas"?
       title = glue("Distribution of School Urbanicity\n by College Bound Students: {.x}")) + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text(size = 10),
        axis.title=element_text(size=10))))

college_bound_hist$plots[[1]]
college_bound_hist$plots[[4]]

fs::dir_create(here::here("plots", "college_bound_hist"))


files <- college_bound_hist$year
paths <- here::here("plots", "college_bound_hist", glue("{files}.png"))
paths

walk2(paths, college_bound_hist$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

```{r}
head(four_year)

low_perf_urban <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(plots = pmap(list(year, data), 
  ~ggplot(..2, aes(low_performing, urbanicity)) +
  ggridges::geom_density_ridges(color = "white",
                                fill = "#A9E5C5") +
  theme_minimal(base_size = 10) +
  scale_x_continuous("Percentage of Students", labels = function(x) paste0(x, "%")) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  labs(x = "Percentage of Students", 
       y = "",
       title = glue("Distribution of School Urbanicity\n by Students Scoring Below 15th Percentile on Standardized Tests:\n {.x}")) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10),
        axis.title=element_text(size=10))))

low_perf_urban$plots[[1]]
low_perf_urban$plots[[2]]

fs::dir_create(here::here("plots", "low_perf_urban"))


files <- low_perf_urban$year
paths <- here::here("plots", "low_perf_urban", glue("{files}.png"))
paths

walk2(paths, low_perf_urban$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

```{r}
head(four_year)

size_hist <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(plots = pmap(list(year, data), 
  ~ggplot(..2, aes(college_going)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~size) +
  theme_minimal(base_size = 15) +
  scale_x_continuous("Percentage of Students", labels = function(x) paste0(x, "%")) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  labs(x = "Percentage of Students College Bound",
       y = "Number of Schools",
       title = glue("Distribution of School Enrollment\n by College Bound Students: {.x}")) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text(size = 10),
        axis.title=element_text(size=10))))

size_hist$plots[[1]]
size_hist$plots[[4]]

fs::dir_create(here::here("plots", "size_hist"))


files <- size_hist$year
paths <- here::here("plots", "size_hist", glue("{files}.png"))
paths

walk2(paths, size_hist$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

```{r}
size_density <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(plots = pmap(list(year, data), 
  ~ggplot(..2, aes(low_performing, size)) +
  ggridges::geom_density_ridges(color = "white",
                                fill = "#A9E5C5") +
  theme_minimal(base_size = 10) +
  scale_x_continuous("Percentage of Students", labels = function(x) paste0(x, "%")) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(color = "gray80")) +
  labs(x = "Percentage of Students", 
       y = "",
       title = glue("Distribution of School Enrollment\n by Students Scoring Below 15th Percentile on Standardized Tests:\n {.x}")) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10),
        axis.title=element_text(size=10))))

size_density$plots[[1]]
size_density$plots[[2]]

fs::dir_create(here::here("plots", "size_density"))


files <- size_density$year
paths <- here::here("plots", "size_density", glue("{files}.png"))
paths

walk2(paths, size_density$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

```{r}
head(batch)
head(four_year)

r_tbl <- four_year %>% 
  select(year, urbanicity, size, low_performing, college_going) %>% 
  reactable(columns = list(
    year = colDef(name = "Year"),
    urbanicity = colDef(name = "School Urbanicity"),
    size = colDef(name = "School Enrollment"),
    low_performing = colDef(name = "Percentage of Low Performing Students"),
    college_going = colDef(name = "Percentage of College Bound Students")
  ),
   height = 500,
   striped = TRUE, 
   compact = TRUE, 
   outlined = TRUE,
   searchable = TRUE)

r_tbl

urban_totals <- four_year %>% 
  group_by(year, urbanicity) %>% 
  summarize(n=n()) %>% 
  na.omit() %>% 
  reactable(columns = list(
    year = colDef(name = "Year"),
    urbanicity = colDef(name = "School Urbanicity"),
    n = colDef(name = "Total")
  ),
   height = 500,
   striped = TRUE, 
   compact = TRUE, 
   outlined = TRUE,
   searchable = TRUE)

urban_totals

size_totals <- four_year %>% 
  group_by(year, size) %>% 
  summarize(n=n()) %>% 
  na.omit() %>% 
  reactable(columns = list(
    year = colDef(name = "Year"),
    size = colDef(name = "School Enrollment"),
    n = colDef(name = "Total")
  ),
   height = 500,
   striped = TRUE, 
   compact = TRUE, 
   outlined = TRUE,
   searchable = TRUE)

size_totals
```


```{r}
head(four_year)

year_ind <- four_year %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(mod1 = map(data, ~lm(total ~ urbanicity, data = .x)),
         mod2 = map(data, ~lm(total ~ size, data = .x)), 
          mod3 = map(data, ~lm(total ~ urbanicity + size, data = .x)))

# Just an experiment: I can imagine that size will affect rate of crime more than urbanicity does, how about control for size?

year_ind$mod1[[1]]
year_ind$mod2[[1]]
year_ind$mod3[[1]]

comp <- anova(year_ind$mod1[[1]], year_ind$mod2[[1]], year_ind$mod3[[1]])
comp

year_ind %>% 
  mutate(comp12 = map2(mod1, mod2, anova))

str(comp)

year_ind %>%
    pivot_longer(mod1:mod3, names_to = "model", values_to = "output")

year_ind %>%
    gather(model, output, mod1:mod3) %>%
    mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))

year_ind %>%
    gather(model, output, mod1:mod3) %>%
    mutate(r2 = map_dbl(output, ~summary(.x)$r.squared)) %>%
ggplot(aes(model, r2)) +
    geom_col(aes(fill = model)) +
    facet_wrap(~year) +
    scale_fill_brewer(palette = "Set2") +
  labs(x = "Model",
       y = "r2",
       title = "Model Comparison",
       caption = "Mod1: total incidents predicted by school urbanicity\n  Mod2: total incidents predicted by school enrollment \n Mod3: total incidents predicted by school urbanicity, controlled for school enrollment") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10),
        axis.title=element_text(size=10))

```