---
title: "Preliminary Ideas"
author: "JP"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminary Ideas

```{r}
library(tidyverse)
library(psych)
```


```{r}
safe06 <- safe06 %>% 
  dplyr::select(-c0016_r)

safe08 <- safe08 %>% 
  dplyr::select(-c0016_r)

safe06$year <- c('2005-2006')

safe08$year <- c('2007-2008')

all <- full_join(safe06, safe08)
```

Since we discussed creating models, it might be easier to create scatterplots showing the associations and then have a visual next to it that shows the strength of the correlation. Then our audience can check the listed predictors on a dropdown menu and the outcomes to see each of the associations in scatterpots. Just an idea. 

### Potential Outcomes 
number students involved in insubordination total = c0508
number of removals for insubordination = c0510
insubordination suspension = c0514, this variable is in both datasets
total off school suspensions = outsus08 for 07-08, outsus06 for 05-06, outsus18 for 17-18
percentage of students likely to go to college = c0534
percentage students academic achievement important = c0536

* Can't find c0508, c0510, or co514 in 17-18 data set 

### Potential Predictors
average percentage daily attendance = c0568
school size = fr_size
student counseling/social work = c0178
individual mentoring/tutoring = c0180 - c0181 in 17-18
recreation/student activities = c0182 - can't find in 17-18
provide training/assistance to parents = c0192
program involves parents at school = c0194
parental involvement back to school night = c0196
parent participates parent-teacher conference = c0198
parent participates in subject-area events = c0200 - can't find in 17-18
parent volunteers at school = c0202 - can't find in 17-18

Maybe things changed in coding by the time the 17-18 survey was conducted because I can't find a lot of the variables JP identified in the 05-06 and 07-08. Here are some that seem similar in 17-18:
student involvement in peer mediation = c0175
student involvement in restorative circles = c0179
promote sense of community integration = c0186


### Additional Predictors
1. Percent of minority student enrollment 
  * fr_catmn both data sets 
    * 1 = less than 5 percent
    * 2 = 5 to less than 20 percent
    * 3 = 20 to less than 50 percent
    * 4 = 50 percent or more 

2. School Level
  * fr_lvel in both data sets 
    * 1 = Elementary
    * 2 = Middle
    * 3 = High School (Secondary)
    * 4 = Combined Middle School and High School
    
3. School Urbanicity 
  * fr_urban for both data sets
  * 1 = City
  * 2 = Suburb (coded as "urban fringe" in 05-06 data set)
  * 3 = Town
  * 4 = Rural 

4. Size (fr_size) levels
  * 1 = < 300
  * 2 = 300 - 499
  * 3 = 500 - 999
  * 4 1,000 or more