---
title: "Preliminary Ideas"
author: "JP"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminary Ideas

```{r}
library(tidyverse)
library(psych)
```


```{r}
safe06 <- safe06 %>% 
  dplyr::select(-c0016_r)

safe08 <- safe08 %>% 
  dplyr::select(-c0016_r)

safe06$year <- c('2005-2006')

safe08$year <- c('2007-2008')

all <- full_join(safe06, safe08)
```

Since we discussed creating models, it might be easier to create scatterplots showing the associations and then have a visual next to it that shows the strength of the correlation. Then our audience can check the listed predictors on a dropdown menu and the outcomes to see each of the associations in scatterpots. Just an idea. 

### Potential Outcomes 
number students involved in insubordination total = c0508
number of removals for insubordination = c0510
insubordination suspension = c0514, this variable is in both datasets
total off school suspensions = outsus08 for 07-08, outsus06 for 05-06
percentage of students likely to go to college = c0534
percentage students academic achievement important = c0536

### Potential Predictors
average percentage daily attendance = c0568
school size = fr_size
student counseling/social work = c0178
individual mentoring/tutoring = c0180
recreation/student activities = c0182
provide training/assistance to parents = c0192
program involves parents at school = c0194
parental involvement back to school night = c0196
parent participates parent-teacher conference = c0198
parent participates in subject-area events = c0200
parent volunteers at school = c0202

